---
title: "Covid91 vaccine study Final2022"
author: "Eden Williams"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final_Data.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
Males=filter(FinalData, sex=="M")
Females=filter(FinalData, sex=="F")
LGBTQ=filter(FinalData, LGBTQ=="gay")
Drugs=filter(FinalData, DrugUser=="yes")
```

# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.


$H_0$:The effectivness of the drug remains the same across each subgroup


$H_A$:The effectiveness of the drug changes depending on the subgroup



## Methods 

Since the variables we are looking at are all categorical we will be using CAT-CAT method. This means we will be looking at a bar chart graph as well as performing a chi-squared and fisher exact test. These methods will help us gather our evidence. 


# Males


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~ infected+ treatment,data=Males)
barchartGC(~infected  + treatment ,data=Males, type="percent")
```

Based off of the barcharts here, we can see that among males those who took the vaccine contracted covid at a lesser rate than those that took the placebo. 


### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=Males)
rowPerc(table1)
colPerc(table1)
```

Here we can see that of the males that took the vaccine, 32% contracted covid while 67% who took the placebo contracted covid. The males that took the placebo are 2.63 times more likely to contract covid as opposed to those that took the vaccine. 









## Inferential Results


```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```






## Efficacy 


# Females


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~ infected+ treatment,data=Females)
barchartGC(~infected  + treatment ,data=Females, type="percent")
```

Based off of the barchart here, we can see that for females, the vaccine does seem to prevent them from getting covid. The percentage of those who contracted covid is much less that those who took the placebo.  



### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=Females)
rowPerc(table1)
colPerc(table1)
```

From these results, we can see that out of the women that received the vaccine, 41% of them contracted covid as opposed to the 58% who contracted covid while taking the placebo. This means that taking the placebo makes women 2.3 times more likely to contract covid. 





## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Based of the results from the chi-squared and fisher exact test, we can conclude that the vaccine is effective for women. We can tell this because the p-value from the chi- squared test is 0.0011 which is below 0.05. We can also tell because the fisher exact test shows us that those who take the placebo are 1.43 times more likely to contract covid.







## Efficacy 













# LGBTQ


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~ infected+ treatment,data=LGBTQ)
barchartGC(~infected  + treatment ,data=LGBTQ, type="percent")
```

From this bar chart it looks like those who are a part of the LGBTQ community and took the vaccine are more likely to contract covid than those that took the placebo. 


### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=LGBTQ)
rowPerc(table1)
colPerc(table1)
```

Here we can see that amoung the LGBTQ folks who took the vaccine 87% of the them ended up getting covid, while only 13% who took the placebo ended up getting covid. Those who took the vaccine are 3 times more likely to contract covid than those who don't.







## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Based off of the results from the chi squared and fisher exact tests we can see that the vaccine is not effective for the LGBTQ community. We can tell because the p-value from the chi- squared test is below 0.05 and the fisher exact test shows us that those who took the placebo are 0.178 times more likely to get covid, which is extremely low. 






## Efficacy 












# Druggies


## Descriptive Results

### Graphical Descriptive Results
```{r}
barchartGC(~ infected+ treatment,data=Drugs)
barchartGC(~infected  + treatment ,data=Drugs, type="percent")
```

Based off the graphs here we can see that for drug users the vaccine actually makes them more susceptible to getting covid than taking the placebo.



### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=Drugs)
rowPerc(table1)
colPerc(table1)
```

Here we can see that of the drug users, 85% who took the vaccine ended up with covid while only 15% who took the placebo ended up with covid. Those who took the vaccine are 3.28 times more likely to contract the virus.  


## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


Based off of the results from the chi-squared test we can see that the vaccine is not effective for drug users and actually puts them more at risk for contracting covid. We can tell because the p-value from the chi squared test is below 0.05 which means that there is not enough evidence to prove that is helpful and the odds ratio from the fisher exact test shows that users who take the placebo are 0.178 times more likely to get covid from taking the placebo, which is extremely low. 



## Efficacy 












