---
title: "Covid91 vaccine study Final2022"
author: "Eden Williams"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="final_Data.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
Males=filter(FinalData, sex=="M")
Females=filter(FinalData, sex=="F")
LGBTQ=filter(FinalData, LGBTQ=="gay")
Drugs=filter(FinalData, DrugUser=="yes")
```

# Introduction

A new  preventative vaccine (covid91) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.


$H_0$:The effectivness of the drug remains the same across each subgroup


$H_A$:The effectiveness of the drug changes depending on the subgroup



## Methods 

Since the variables we are looking at are all categorical we will be using CAT-CAT method. This means we will be looking at a bar chart graph as well as performing a chi-squared and fisher exact test. These methods will help us gather our evidence. 


# Males


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~ infected+ treatment,data=Males)
barchartGC(~infected  + treatment ,data=Males, type="percent")
```




### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=Males)
rowPerc(table1)
colPerc(table1)
```











## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```





## Efficacy 


# Females


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~ infected+ treatment,data=Females)
barchartGC(~infected  + treatment ,data=Females, type="percent")
```





### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=Females)
rowPerc(table1)
colPerc(table1)
```


## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```





## Efficacy 













# LGBTQ


## Descriptive Results

### Graphical Descriptive Results

```{r}
barchartGC(~ infected+ treatment,data=LGBTQ)
barchartGC(~infected  + treatment ,data=LGBTQ, type="percent")
```

From this bar chart it looks like those who are a part of the LGBTQ community and took the vaccine are more likely to contract it than those that took the placebo. 


### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=LGBTQ)
rowPerc(table1)
colPerc(table1)
```




## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```




## Efficacy 












# Druggies


## Descriptive Results

### Graphical Descriptive Results
```{r}
barchartGC(~ infected+ treatment,data=Drugs)
barchartGC(~infected  + treatment ,data=Drugs, type="percent")
```

Based off the graphs here we can see that for drug users the vaccine actually makes them more susceptible to getting covid than taking the placebo.



### Numerical Descriptive Results

```{r}
table1 <- xtabs(~infected + treatment, data=Drugs)
rowPerc(table1)
colPerc(table1)
```

Here we can see that of the drug users, 85% who took the vaccine ended up with covid while only 15% who took the placebo ended up with covid. 


## Inferential Results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```


Based off of the results from the chi-squared test we can see that the vaccine is not effective for drug users and actually puts them more at risk for contracting covid. We can tell because the p-value from the chi squared test is below 0.05 which means that there is not enough evidence to prove that is helpful and the odds ratio from the fisher exact test shows that users who take the placebo are 0.178 times more likely to get covid from taking the placebo, which is extremely low. 



## Efficacy 












